iterSim

### 2023-02-08 analyses/simpleSim.Rmd
checkpoint

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 1,z2=1,z3=1),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]

@@

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 0.5,z2=0.5,z3=0.5),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]
  train<-data
  #test<-data[-samp,-c(ncol(data))]
  #fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )

  ##########################
  ###DSM
  ##########################
  source_python('src/dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times,tPos=ncol(train)-2,ePos=ncol(train)-1)
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    next
  }
  colnames(dsmSurv) <-times
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

@@

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # 
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
    source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)
  # source_python('src/deephitter.py')
  # hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # hitnnSurv<-t(hitnnSurv)
  # colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  # deephitCleaned<-pyProcess(hitnnSurv,times=times)
  # colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  # py_run_string("del fitDeephit")
  # rm(fitDeephit)
  # 
  ############################
  ###PMNNsplines
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          #val_split=0.2,
                          min_delta=min_delta,
                          patience=patience,val=valcbtensor)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-1,1))

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 100
  patience: 10
  iteration: 1
  layer1: 100
  layer2: 100
  layer3: 50
  layer4: 50
  drpt: 0.1
  lr: 0.001
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta =10^-7
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-3*15#as.numeric(params$layer1)
layer2<-3*15#as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)
lr=as.numeric(params$lr)
paramTrials<-readRDS("complexTrials.rds") 
lr<-paramTrials[which.max(paramTrials$integBrier),]$lr
layer1<-paramTrials[which.max(paramTrials$integBrier),]$layer1
layer2<-paramTrials[which.max(paramTrials$integBrier),]$layer2
layer3<-3*5#as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-paramTrials[which.max(paramTrials$integBrier),]$drpt
bsize=paramTrials[which.max(paramTrials$integBrier),]$bsize
activ<-paramTrials[which.max(paramTrials$integBrier),]$actv

lr<-paramTrials[which.min(paramTrials$valLoss),]$lr
layer1<-paramTrials[which.min(paramTrials$valLoss),]$layer1
layer2<-paramTrials[which.min(paramTrials$valLoss),]$layer2
layer3<-3*5#as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-paramTrials[which.min(paramTrials$valLoss),]$drpt
bsize=paramTrials[which.min(paramTrials$valLoss),]$bsize
activ<-paramTrials[which.min(paramTrials$valLoss),]$actv

@@

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 0.05,z2=1.5,z3=0.5),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]

@@

  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5))
  )

  dat <- simsurv(dist = "exponential",
                 lambdas =.05,
                 betas = c(z1 = 0.5,z2=0.5,z3=0.5),
                 x = cov,
                 tdefunction = "log",
                 maxt = 1
  )
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]
  train<-data

  sds<-sapply(train, function(x) (sd(x)))
means<-sapply(train, function(x) (mean(x)))
test<-normalizer(res$test,means,sds)[,-c(ncol(data))]
fullTest<-normalizer(res$test,means,sds)
val<-normalizer(res$validate,means,sds)

train<-normalizer(train,means,sds)
  #test<-data[-samp,-c(ncol(data))]
  #fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )

  ##########################
  ###DSM
  ##########################
  source_python('src/dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=test,bsize=floor(nrow(train)/100),epochs=20,val=val,times=times,tPos=ncol(train)-2,ePos=ncol(train)-1,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=floor(nrow(train)/100),epochs=epo,val=val,times=times,tPos=ncol(train)-2,ePos=ncol(train)-1,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    next
  }
  colnames(dsmSurv) <-times
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

@@

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # 
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
    source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,floor(nrow(train)/100),epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)
  # source_python('src/deephitter.py')
  # hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # hitnnSurv<-t(hitnnSurv)
  # colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  # deephitCleaned<-pyProcess(hitnnSurv,times=times)
  # colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  # py_run_string("del fitDeephit")
  # rm(fitDeephit)
  # 
  ############################
  ###PMNNsplines
  ############################  
    valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    #layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    #layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=floor(nrow(mod_cb_glm$data)/100),
                          verbose=0,
                          monitor="val_loss",
                          #val_split=0.2,
                          min_delta=min_delta,
                          patience=patience,val=valcbtensor)

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    #layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    #layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=floor(nrow(mod_cb_glm$data)/100),
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-.5,.5))
